A comparison of design-based and model-based approaches for finite population spatial data.

### 2021-12-22 inst/manuscript/manuscript.tex
added running header

\usepackage{bm} \usepackage{bbm} \usepackage{color} \DeclareMathOperator{\var}{{var}} \DeclareMathOperator{\cov}{{cov}} \usepackage{caption} \usepackage{subcaption} \usepackage{setspace} \doublespacing

>>>>

\usepackage{bm} \usepackage{bbm} \usepackage{color} \DeclareMathOperator{\var}{{var}} \DeclareMathOperator{\cov}{{cov}} \usepackage{caption} \usepackage{subcaption} \usepackage{setspace} \usepackage{fancyhdr}

\pagestyle{fancy} \fancyhf{} \chead{Spatial design-based vs model-based}
\doublespacing
